Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-07-08 doc/PRF2022/PRF_main.tex
fixed bibliography

The many-body hydrodynamics of amphiphilic Janus particles (JP) suspended in a viscous fluid (at zero Reynolds number) has been studied using
boundary integral numerical simulations \cite{fu-qua-ryh-you}. Janus particles consist of both a hydrophobic and a hydrophilic surfaces. 
Immersed in a viscous solvent, the dynamics of a JP suspension results from the combination of long-range hydrodynamic interaction and non-local
interactions between JPs through the distribution of a hydrophobic potential (HAP). In a quiescent flow, numerical simulations of a 
JP suspension showed self-assembly into micelles and bilayers of JPs that provide an alternative means for computing the 
mechanical moduli of a colloidal membrane.

Under background flows, the hydrodynamics of a JP vesicle (a self-enclosed bilayer of JPs) exhibit many familiar behaviors of a vesicle \cite{fu-qua-ryh-you}: 
Elongation and alignment along the extensional direction, tank-treading, and rupture of a vesicle under shear flow.

@@

Variation of the
the free energy \eqref{eq:free_energy}
provides
\begin{equation}
  \FF_i = \int_{\Gamma_i} \mathbf{T}\nnu \, \dif s
  - \frac{M}{\rho_0}
  \sum_{j \neq i}
  \frac{\aa_i - \aa_j}{|\aa_i - \aa_j|}
P'\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right)
  ,\quad
T_i = \int_{\Gamma_i} (\xx - \aa_i)^{\perp}\cdot (\mathbf{T}\nnu) \, \dif s, 
\end{equation}
for $i = 1,\dots,N_b$. The term 
$
\mathbf{T}
= \gamma \left[ \rho^{-1} u^2 \mathbf{I}
  + \rho \left(|\nabla u|^2 \mathbf{I} - 2\nabla u \nabla u^T\right)\right]
$
is the hydrophobic stress identified in ~\cite{Fu2018_SIAM} 
and derived by variation of the domain techniques.

@@

In Figure~\ref{fig:Ves_shear} (a)--(c), the vesicle in a shear flow undergoes the familiar tank-treading deformation. 
Our previous paper \cite{fu-qua-ryh-you} studied the geometry,
intermonolayer slip, and critical shear rates $\gamma^*=0.066$
for vesicles comprised of amphiphilic Janus particles. 
Here $\dot\gamma=0.05, 0.066, 0.075$ and there are jumps in energies (Figure \ref{fig:Ves_shear}d, long and short dashed curves) due to the breaking of the vesicle into two
components. There is greater variation in the order parameter $\tilde{S}_2(t)$ as well
with a baseline value around $0.7$
(Figure \ref{fig:Ves_shear}e, dashed curve).
The oscillations occur due to the orbit of the two bilayer components, and $\tilde{S}_2(t)$ increases to about $0.9$ when the components are nearly parallel and slide past one another.
For the lowest shear rate case, it has nearly perfect orientational parameter due to the steady tank-treading motion.
Positional order, however, diverges since the two component configuration
is uncorrelated to the initial circular configuration (Figure \ref{fig:Ves_shear}f, dashed curve).

@@

%%%
\subsection{Hydrophobic Attraction Potential Mobility Problem} 
The mathematical formulation is a nonlinear system for the dynamics of a
collection of rigid Janus particles. For the sake of completeness, we
summarize the governing equations here, and a complete description is in
our previous work~\cite{fu-qua-ryh-you2022}. The interactions satisfy a
system of partial differential equations (PDEs) that describe the
hydrodynamic interactions and hydrophobic interactions. Assuming
inertial terms are negligible, the solvent is goverened by the Stokes
equations
\begin{alignat}{3}
\label{eq:stokes}
  -\mu \Delta \uu + \nabla p &= \mathbf{0},     && \xx \in \Omega, \\
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
\end{alignat}
where $\uu$ is the velocity, $p$ is the pressure, $\uu_\infty$ is the
background flow, and $\mu$ is the constant viscosity. The domain $\Omega
= \Omega(t)$ is the fluid region surrounding the particles and changes
shape as the particles move. Since the particles are rigid, the solvent
velocity satisfies the no-slip rigid body motion boundary condition
\begin{align}
  \vv_i + \omega_i (\xx - \aa_i)^\perp = \uu(\xx), 
    \quad \xx \in \Gamma_i,
\end{align}
where $\vv_i$ is the translational velocity and $\omega_i$ is the
angular velocity. Once these velocities are determined, we use
second-order Adams-Bashforth to update the particle configuration.

@@

\end{document}
%
% ****** End of file apstemplate.tex ******

>>>>

The many-body hydrodynamics of amphiphilic Janus particles (JP) suspended in a viscous fluid (at zero Reynolds number) has been studied using
boundary integral numerical simulations \cite{Fu2022_JFM}. Janus particles consist of both a hydrophobic and a hydrophilic surfaces. 
Immersed in a viscous solvent, the dynamics of a JP suspension results from the combination of long-range hydrodynamic interaction and non-local
interactions between JPs through the distribution of a hydrophobic potential (HAP). In a quiescent flow, numerical simulations of a 
JP suspension showed self-assembly into micelles and bilayers of JPs that provide an alternative means for computing the 
mechanical moduli of a colloidal membrane.

Under background flows, the hydrodynamics of a JP vesicle (a
self-enclosed bilayer of JPs) exhibit many familiar behaviors of a
vesicle \cite{Fu2022_JFM}: 
Elongation and alignment along the extensional direction, tank-treading, and rupture of a vesicle under shear flow.

@@

Variation of the
the free energy \eqref{eq:free_energy}
provides
\begin{equation}
  \FF_i = \int_{\Gamma_i} \mathbf{T}\nnu \, \dif s
  - \frac{M}{\rho_0}
  \sum_{j \neq i}
  \frac{\aa_i - \aa_j}{|\aa_i - \aa_j|}
P'\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right)
  ,\quad
T_i = \int_{\Gamma_i} (\xx - \aa_i)^{\perp}\cdot (\mathbf{T}\nnu) \, \dif s, 
\end{equation}
for $i = 1,\dots,N_b$. The term 
$
\mathbf{T}
= \gamma \left[ \rho^{-1} u^2 \mathbf{I}
  + \rho \left(|\nabla u|^2 \mathbf{I} - 2\nabla u \nabla u^T\right)\right]
$
is the hydrophobic stress identified in ~\cite{Fu20} 
and derived by variation of the domain techniques.

@@

In Figure~\ref{fig:Ves_shear} (a)--(c), the vesicle in a shear flow undergoes the familiar tank-treading deformation. 
Our previous paper \cite{Fu2022_JFM} studied the geometry,
intermonolayer slip, and critical shear rates $\gamma^*=0.066$
for vesicles comprised of amphiphilic Janus particles. 
Here $\dot\gamma=0.05, 0.066, 0.075$ and there are jumps in energies (Figure \ref{fig:Ves_shear}d, long and short dashed curves) due to the breaking of the vesicle into two
components. There is greater variation in the order parameter $\tilde{S}_2(t)$ as well
with a baseline value around $0.7$
(Figure \ref{fig:Ves_shear}e, dashed curve).
The oscillations occur due to the orbit of the two bilayer components, and $\tilde{S}_2(t)$ increases to about $0.9$ when the components are nearly parallel and slide past one another.
For the lowest shear rate case, it has nearly perfect orientational parameter due to the steady tank-treading motion.
Positional order, however, diverges since the two component configuration
is uncorrelated to the initial circular configuration (Figure \ref{fig:Ves_shear}f, dashed curve).

@@

%%%
\subsection{Hydrophobic Attraction Potential Mobility Problem} 
The mathematical formulation is a nonlinear system for the dynamics of a
collection of rigid Janus particles. For the sake of completeness, we
summarize the governing equations here, and a complete description is in
our previous work~\cite{Fu2022_JFM}. The interactions satisfy a
system of partial differential equations (PDEs) that describe the
hydrodynamic interactions and hydrophobic interactions. Assuming
inertial terms are negligible, the solvent is goverened by the Stokes
equations
\begin{alignat}{3}
\label{eq:stokes}
  -\mu \Delta \uu + \nabla p &= \mathbf{0},     && \xx \in \Omega, \\
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
\end{alignat}
where $\uu$ is the velocity, $p$ is the pressure, $\uu_\infty$ is the
background flow, and $\mu$ is the constant viscosity. The domain $\Omega
= \Omega(t)$ is the fluid region surrounding the particles and changes
shape as the particles move. Since the particles are rigid, the solvent
velocity satisfies the no-slip rigid body motion boundary condition
\begin{align}
  \vv_i + \omega_i (\xx - \aa_i)^\perp = \uu(\xx), 
    \quad \xx \in \Gamma_i,
\end{align}
where $\vv_i$ is the translational velocity and $\omega_i$ is the
angular velocity. Once these velocities are determined, we use
second-order Adams-Bashforth to update the particle configuration.

@@
